\chapter{The Charities and Arts Sponsorship Funds} \label{App:CharitiesArtsFunds}
\section{The Charities Sponsorship Fund and Junior Members Charities Committee} \label{AppSec:CharitiesFunc}
\appnpara The purpose of the Charities Sponsorship Fund (henceforth, the ``Sponsorship Fund") is to support Junior Members in the pursuit of charitable causes.
\appnpara The Merton College Junior Members Charities Committee (henceforth ``the Charities Committee") shall have the authority to make donations from the Sponsorship Fund. For advice concerning applications to the Sponsorship Fund, Junior Members are referred to the Charities Representative of their respective Common Room.
\appnpara The Charities Committee shall consist of the President, Treasurer, and Charities Representative of the JCR, and the same of the MCR, and shall meet at least once a term. The Charities Committee shall be co-chaired by the Charities Representatives of the JCR and MCR, and each Common Room shall have three votes. Quorum for a Charities Committee meeting shall be all six members present and voting. There shall be no abstentions from a vote, and an application requires more votes in favour than against to pass. JCR and MCR Representatives on the Charities Committee serve ex officio on said Committee and it shall be permissible for their votes to be directed by their respective Common Room according to its rules.
\appnpara Applications for the Sponsorship Fund should be completed on the form available on the JCR website or from one of the Charities Representatives, and presented to that Charities Representative no later than two days before the Charities Committee meeting. The form shall be completed by the applicant, presented to the Charities Representative, and considered by the Charities Committee. The Charities Committee shall review its application and approval process annually in its meeting in Hilary Term.
\appnpara The maximum amount that can be granted to any one Junior Member in any one application is £200, or in exceptional circumstances £500. Applications must show that other sources of funding are also being sought, and grants from the Sponsorship Fund may not be more than 50\% of the total raised for the activity. The distribution of the Sponsorship Fund rests with the Charities Committee.
\appnpara Extraordinary Meetings of the Charities Committee may be summoned by a simple majority resolution in the General Meeting of either the JCR or the MCR. There shall be two possible reasons for an Extraordinary Meeting: a) to consider an urgent application, the timing of which results from no fault of the applicant or b) to reconsider an application rejected by the immediately preceding Charities Committee meeting. An Extraordinary Meeting shall run along the same lines as detailed in paragraph 3 of this Appendix.
\appnpara Preference shall be given to those Junior Members who have not previously applied to the Sponsorship Fund over those who have, though there is no limit on the number of times a Junior Member may apply for grants from the Sponsorship Fund.
\appnpara The Charities Representatives and the Treasurers shall be responsible for publishing termly accounts of Sponsorship Fund expenditure to their respective Common Rooms.  The Charities Representatives shall request feedback material from successful applications to be posted on Common Room noticeboards to ensure Junior Members are aware of how Sponsorship Fund expenditure has been used.
\appnpara The content of Section 1 of this Appendix may only be altered with the approval of the General Meeting of both the JCR and the MCR.

\section{The Arts Sponsorship Fund} \label{AppSec:ArtsFund}
\npara The purpose of the Arts Sponsorship Fund (henceforth, the "Arts Fund”) is to support Junior Common Room Members in the promotion of artistic endeavors. Junior Common Room Members   
\npara The Merton College Junior Common Room Arts Committee (henceforth “the Arts Committee”) shall have the authority to make donations from the Arts Fund. For advice concerning applications to the Arts Fund, JCR Members are referred to the JCR Arts and Culture Representative.   
\npara The Arts Committee shall consist of the President, Treasurer, and Arts and Culture Representative of the JCR, and shall meet in 5th Week. The Arts Committee shall be chaired by the Arts and Culture Representative of the JCR. Quorum for the Arts Committee meeting shall be all three members present and voting. There shall be no abstentions from a vote, and an application requires more votes in favour than against to pass. JCR Representatives on the Arts Committee serve ex officio on said Committee and it shall be permissible for their votes to be directed by their respective Common Room according to its rules.   
\npara Applications for the Arts Fund should be completed on the form available on the JCR website or from the Arts and Culture Representative, and presented to that Arts and Culture Representative no later than two days before the Arts Committee meeting by Wednesday 4th Week. The form shall be completed by the applicant, presented to the Arts and Culture Representative, and considered by the Arts Committee. The Arts Committee shall review its application and approval process annually in its meeting in Hilary Term.   
\npara Applications should be made by JCR Members on behalf of a production or artistic project and should be made in conjunction with other JCR Members who are involved in the same project and requesting funding. Projects with more Merton JCR Members will be prioritised for funding. Preference shall be given to those Junior Members who have not previously applied to the Arts Fund over those who have, though there is a limit of one application per term on the number of times a JCR Member may apply for grants from the Arts Fund. The distribution of the Arts Fund rests with the Arts Committee.   
\npara Extraordinary Meetings of the Arts Committee may be summoned by the discretion of the JCR President, Treasurer or Arts and Culture Representative. There shall be two possible reasons for an Extraordinary Meeting: a) to consider an urgent application, the timing of which results from no fault of the applicant or b) to reconsider an application rejected by the immediately preceding Arts Committee meeting. An Extraordinary Meeting shall run along the same lines as detailed in paragraph 3 of this Appendix.   
\npara The Arts and Culture Representatives and the Treasurers shall be responsible for publishing termly accounts of Arts Fund expenditure to their respective Common Rooms. The Arts and Culture Representative shall request feedback material from successful applications to be posted on Common Room noticeboards to ensure JCR Members are aware of how Arts Fund expenditure has been used.   
\npara This Appendix may only be altered with the approval of the General Meeting of the JCR.  
